---
title: "Settling data processing"
output: html_document
date: '2022-09-27'
author: "Vibeke S. Nielsen"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Save data to
```{r}
path_out<- "D://Speciale/Data/Broad_inspection/"
fileName <- paste(path_out, "Viborg100.csv", sep = "")
testName <- "Viborg"
```



#Defining parameters
```{r}
SS <-   4.57      #[g/L]
Dilution.percent <-100 #[%]
n <- 1 #Dilution_factor

```




#Install packages
```{r}
library(data.table)
library(readxl)
library(tidyverse)
library(ggplot2)
library(plyr)
library(dplyr)


```


#Load settling data and quick visualisation in heatmap
```{r}
d<- openxlsx::read.xlsx( "D://Speciale/Data/Broad_inspection/DATALOGviborg.xlsx", sheet = "100")
```

```{r}
d1<- column_to_rownames(d, var = "Timestamp")
d1_matrix <- as.matrix(d1)
heatmap(d1_matrix, Colv=NA, Rowv=NA,scale = "column", 
        ylab = "Time [min]", xlab= "Sensor")

```

#Creating graph
Need to define the movement of the sludge mirror height. This is obtained by finding the timestamp for the biggest difference between two data points for a sensor. By that we find at which time the sludge mirror is at the sensor, when the light goes from being blocked by high turbidity to going through a clear water.

```{r}
#Finding difference between rows
rows <- nrow(d)
diff_rows <- d[-rows,] - d[-1,]
diff_rows <- rbind(c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), diff_rows)

#The slope is an expression of the biggest difference between two sensor measurements. The slope is found by dividing with time difference
slope <- diff_rows[]/diff_rows$Timestamp

#Adding timestamp column (making the dataframe work for next step)
slope <- subset.data.frame(slope, select=-Timestamp)
slope_to_time <- cbind(d$Timestamp, slope)
colnames(slope_to_time)[1]<- "Timestamp"

#Visualizing in heatmap
s.t_matrix <- as.matrix(slope_to_time)
heatmap(s.t_matrix, Colv=NA, Rowv=NA,scale = "column")
```


##Finding minimum value for each sensor and coupling it to timestamp
```{r}
minLDR <- apply(slope, 2, function(x) which.min(x))
Sensor_no. <- names(slope_to_time)[-1]
ready.file <- data.frame(slope_to_time[minLDR,1], Sensor_no.)
colnames(ready.file)[1]<- "Timestamp"


blanketheight <- merge(slope_to_time, ready.file, all=TRUE)
blanketheight <- blanketheight[,c("Timestamp","Sensor_no.")]
#always increasing timestamp: copying previous value, if below
#ready.file$Timestamp <- ave(ready.file$Timestamp, FUN = cummax)

#Load cylinder dimensions
Cyl_dim <- openxlsx::read.xlsx("D://Speciale/Data/Cylinder_dimensions.xlsx")
colnames(Cyl_dim)[1]<- "Sensor_no."
colnames(Cyl_dim)[2]<- "Height"
colnames(Cyl_dim)[3]<- "Volume"

#merger cylinderhøjden ind for hvert timestamp
blanketheight <- merge(blanketheight, Cyl_dim, all.x=TRUE)
#sorterer rækker efter stigende tid
blanketheight <- blanketheight[order(blanketheight$Timestamp),]

install.packages("zoo")              
library("zoo") 
#Udfylder NA med værdi i tidligere række
blanketheight <- na.locf(blanketheight)
```
##Create plot
```{r}
#plot 
ggplot(blanketheight, aes(Timestamp, Height)) + 
  geom_point()+ labs(x="Time [s]", y="Sludge blanket height [mm]", )

```
#Write out blanketheight to csv file
```{r}
write.csv(blanketheight, fileName)
```
#Alternative to finding steepest slope for velocity
```{r}
#subset to hindered settling phase and exclude outliers
hin_settling <- blanketheight[blanketheight$Height <300, ]
hin_settling <- hin_settling[hin_settling$Height >100, ]


#find difference between every 5th row (70 s)
diff_by5 <- diff(as.matrix(hin_settling$Height), lag = 5)
max_diff_value <- apply(diff_by5, 2, function(x) min(x))
#get the index where the max difference is present
max_diff_index <- apply(diff_by5, 2, function(x) which.min(x))
#make dataframe spanning 5 steepest datapoints
max_slope_span <- max_diff_index +5L
max_slope <-  hin_settling[max_diff_index:max_slope_span,]

#determining slope
velocity.slope <- coef(lm(max_slope$Height~max_slope$Timestamp))[2]
velocity<- velocity.slope*(-1)
Velocity.intercept <- coef(lm(max_slope$Height~max_slope$Timestamp))[1]

#creating plot with slope
ggplot(blanketheight, aes(Timestamp, Height)) + 
  geom_point()+ 
  labs(x="Time [s]", y="Sludge blanket height [mm]")+ geom_abline(intercept = Velocity.intercept, slope = velocity.slope
,color="blue")

```

#Determining settling velocity
##Find slope for hindered settling phase 
```{r}
#subsetting to remove LDR1 and LDR2 due to filling of column
#hin_settling <- blanketheight[blanketheight$Height <300, ]
#removing odd datapoints 
#hin_settling <- hin_settling[hin_settling$Height >100, ]

#creating plot
#ggplot(hin_settling, aes(Timestamp, Height)) + 
#  geom_point()+ 
#  labs(x="Time [s]", y="Sludge blanket height [mm]")
 

#subsetting to hindered settling phase
#hin_settling <- hin_settling[hin_settling$Timestamp <300, ]

#creating plot
#ggplot(hin_settling, aes(Timestamp, Height)) + 
#  geom_point()+ 
#  labs(x="Time [s]", y="Sludge blanket height [mm]")+ 
#  geom_smooth(method="lm",se=F, formula = y~x)

#determining slope
#velocity <- coef(lm(hin_settling$Height~hin_settling$Timestamp))[2]
#velocity<- velocity*(-1)
```

#Determining Diluted Sludge Volumen Index
$DSVI=(SV_{30}*n)/SS$ 
```{r}
#visualize volume to time
ggplot(blanketheight, aes(Timestamp, Volume)) + 
  geom_point()+ 
  labs(x="Time [s]", y="Sludge mirror height [mL]")

#Create subset for data at 1800 s
SV30_sub <- blanketheight[blanketheight$Timestamp >1000, ]
SV30_sub <- SV30_sub[SV30_sub$Timestamp <2000, ]
#removing scewing datapoints
SV30_sub <- SV30_sub[SV30_sub$Height >75, ]
#SV30_sub <- SV30_sub[SV30_sub$Height <293, ]

#Finds slope and intercept for Time = 30 min
ggplot(SV30_sub, aes(Timestamp, Volume)) + 
  geom_point()+ 
  labs(x="Time [s]", y="Sludge mirror height [mL]")+ 
  geom_smooth(method="lm",se=F, formula = y~x)

```

##Determing SV$_{30}$
```{r}
SV_30_slope <- coef(lm(SV30_sub$Volume~SV30_sub$Timestamp))[2]
SV_30_intercept <- coef(lm(SV30_sub$Volume~SV30_sub$Timestamp))[1]
SV_30 <- SV_30_slope * 1800 + SV_30_intercept
SV_30
```

##Determining DSVI
```{r}
DSVI <- SV_30 * n/ SS
DSVI
```

#Gather parameters in table
```{r}
Parameters<- read.csv( "D://Speciale/Data/Broad_inspection/Collected_parameters_process.csv")

Parameters<-Parameters[,2:12]

Parameters[nrow(Parameters)+1,] <-c(testName,Dilution.percent,n,SS,velocity,SV_30_intercept,SV_30_slope,SV_30,DSVI,Velocity.intercept,velocity.slope)
parameterName <- paste(path_out, "Collected_parameters_process.csv", sep = "")


```


```{r}
write.csv(Parameters, parameterName)
```



# timeseries: https://r-graph-gallery.com/time-series.html

