---
title: "Settling data processing"
output: html_document
date: '2022-09-27'
author: "Vibeke S. Nielsen"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Save data to
```{r}
path_out<- "D://Speciale/Data/Time_series/"
fileName <- paste(path_out, "DAM_28.02.csv", sep = "")
Date <- "28.02.2023"
```


#Load settling data and quick visualisation in heatmap
```{r}
d<- openxlsx::read.xlsx( "D://Speciale/Data/Time_series/Biofos21.02-28.02.xlsx", sheet= "28.02")

Biofos_metadata <- read_excel("D://Speciale/Data/Time_series/Biofos1 metadata.xlsx", col_types = c( "date", "numeric","numeric","numeric", "numeric","numeric","numeric", "text"))

names(Biofos_metadata)[1] <- "Date"
names(Biofos_metadata)[3] <- "Dilutionfactor"
names(Biofos_metadata)[4] <- "SS"
names(Biofos_metadata)[5] <- "DSVI"
names(Biofos_metadata)[6] <- "SV"
names(Biofos_metadata)[7] <- "SVI"
Biofos_metadata$Date <- format(Biofos_metadata$Date, "%d.%m.%Y")

```



#Defining parameters
```{r}
SS <-   Biofos_metadata[(Biofos_metadata[,"Date"]) == Date, "SS"]
SS <- as.numeric(SS)
Dilution.percent <-40 #[%]
n <- 2.5
```




#Install packages
```{r}
library(data.table)
library(readxl)
library(tidyverse)
library(ggplot2)
library(plyr)
library(dplyr)


```

```{r}
d1<- column_to_rownames(d, var = "Timestamp")
d1_matrix <- as.matrix(d1)
heatmap(d1_matrix, Colv=NA, Rowv=NA,scale = "column", 
        ylab = "Time [min]", xlab= "Sensor")

```

#Creating graph
Need to define the movement of the sludge mirror height. This is obtained by finding the timestamp for the biggest difference between two data points for a sensor. By that we find at which time the sludge mirror is at the sensor, when the light goes from being blocked by high turbidity to going through a clear water.

```{r}
#Finding difference between rows
rows <- nrow(d)
diff_rows <- d[-rows,] - d[-1,]
diff_rows <- rbind(c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), diff_rows)

#The slope is an expression of the biggest difference between two sensor measurements. The slope is found by dividing with time difference
slope <- diff_rows[]/diff_rows$Timestamp

#Adding timestamp column (making the dataframe work for next step)
slope <- subset.data.frame(slope, select=-Timestamp)
slope_to_time <- cbind(d$Timestamp, slope)
colnames(slope_to_time)[1]<- "Timestamp"

#Visualizing in heatmap
s.t_matrix <- as.matrix(slope_to_time)
heatmap(s.t_matrix, Colv=NA, Rowv=NA,scale = "column")
```


##Finding minimum value for each sensor and coupling it to timestamp
```{r}
minLDR <- apply(slope, 2, function(x) which.min(x))
Sensor_no. <- names(slope_to_time)[-1]
ready.file <- data.frame(slope_to_time[minLDR,1], Sensor_no.)
colnames(ready.file)[1]<- "Timestamp"


blanketheight <- merge(slope_to_time, ready.file, all=TRUE)
blanketheight <- blanketheight[,c("Timestamp","Sensor_no.")]
#always increasing timestamp: copying previous value, if below
#ready.file$Timestamp <- ave(ready.file$Timestamp, FUN = cummax)

#Load cylinder dimensions
Cyl_dim <- openxlsx::read.xlsx("D://Speciale/Data/Cylinder_dimensions.xlsx")
colnames(Cyl_dim)[1]<- "Sensor_no."
colnames(Cyl_dim)[2]<- "Height"
colnames(Cyl_dim)[3]<- "Volume"

#merger cylinderhøjden ind for hvert timestamp
blanketheight <- merge(blanketheight, Cyl_dim, all.x=TRUE)
#sorterer rækker efter stigende tid
blanketheight <- blanketheight[order(blanketheight$Timestamp),]

install.packages("zoo")              
library("zoo") 
#Udfylder NA med værdi i tidligere række
blanketheight <- na.locf(blanketheight)
```
##Create plot
```{r}
#plot 
blanketheight <- blanketheight[blanketheight$Timestamp <3000, ]
blanketheight <- blanketheight[blanketheight$Height <300, ]
#blanketheight <- blanketheight[blanketheight$Volume >815, ]


ggplot(blanketheight, aes(Timestamp, Height)) + 
  geom_point()+ labs(x="Time [s]", y="Sludge blanket height [mm]")+ ylim(0,320)

```
#Write out blanketheight to csv file
```{r}
write.csv(blanketheight, fileName)
```
#Alternative to finding steepest slope for velocity
```{r}
#subset to hindered settling phase and exclude outliers
hin_settling <- blanketheight[blanketheight$Height <300, ]
hin_settling <- hin_settling[hin_settling$Height >59, ]


#find difference between every 5th row (70 s)
diff_by5 <- diff(as.matrix(hin_settling$Height), lag = 10)
max_diff_value <- apply(diff_by5, 2, function(x) min(x))
#get the index where the max difference is present
max_diff_index <- apply(diff_by5, 2, function(x) which.min(x))
#make dataframe spanning 5 steepest datapoints
max_slope_span <- max_diff_index +10L
max_slope <-  hin_settling[max_diff_index:max_slope_span,]

#determining slope
velocity.slope <- coef(lm(max_slope$Height~max_slope$Timestamp))[2]
velocity<- velocity.slope*(-1)
Velocity.intercept <- coef(lm(max_slope$Height~max_slope$Timestamp))[1]

#creating plot with slope
ggplot(blanketheight, aes(Timestamp, Height)) + 
  geom_point()+ 
  labs(x="Time [s]", y="Sludge blanket height [mm]")+ ylim(0,320)+ geom_abline(intercept = Velocity.intercept, slope = velocity.slope,color="blue")

```

#Determining settling velocity
##Find slope for hindered settling phase 
```{r}
#subsetting to remove LDR1 and LDR2 due to filling of column
#hin_settling <- blanketheight[blanketheight$Height <300, ]
#removing odd datapoints 
#hin_settling <- hin_settling[hin_settling$Height >50, ]

#creating plot
#ggplot(hin_settling, aes(Timestamp, Height)) + 
#  geom_point()+ 
#  labs(x="Time [s]", y="Sludge blanket height [mm]")
 

#subsetting to hindered settling phase
#hin_settling <- hin_settling[hin_settling$Timestamp <175, ]

#creating plot
#ggplot(hin_settling, aes(Timestamp, Height)) + 
#  geom_point()+ 
#  labs(x="Time [s]", y="Sludge blanket height [mm]")+ 
#  geom_smooth(method="lm",se=F, formula = y~x)

#determining slope
#velocity <- coef(lm(hin_settling$Height~hin_settling$Timestamp))[2]
#velocity<- velocity*(-1)
```

#Determining Diluted Sludge Volumen Index
$DSVI=(SV_{30}*n)/SS$ 
```{r}
#visualize volume to time
ggplot(blanketheight, aes(Timestamp, Volume)) + 
  geom_point()+ 
  labs(x="Time [s]", y="Sludge mirror height [mL]")

#Create subset for data at 1800 s
SV30_sub <- blanketheight[blanketheight$Timestamp >500, ]
SV30_sub <- SV30_sub[SV30_sub$Timestamp <2000, ]
#removing scewing datapoints
SV30_sub <- SV30_sub[SV30_sub$Height >59, ]
SV30_sub <- SV30_sub[SV30_sub$Height <300, ]

#Finds slope and intercept for Time = 30 min
ggplot(SV30_sub, aes(Timestamp, Volume)) + 
  geom_point()+ xlim(0,3000)+
  labs(x="Time [s]", y="Sludge mirror height [mL]")+ 
  geom_smooth(method="lm",se=F, formula = y~x)

```

##Determing SV$_{30}$
```{r}
SV_30_slope <- coef(lm(SV30_sub$Volume~SV30_sub$Timestamp))[2]
SV_30_intercept <- coef(lm(SV30_sub$Volume~SV30_sub$Timestamp))[1]
SV_30 <- SV_30_slope * 1800 + SV_30_intercept
SV_30
```

##Determining DSVI
```{r}
DSVI <- SV_30 * n/ SS
DSVI <- as.numeric(DSVI)

```

#Gather parameters in table
```{r}
Parameters<- read.csv( "D://Speciale/Data/Time_series/Biofos_timeseries_parameters.csv")
Parameters<-Parameters[,c("Date","Dilution.percent","n","SS","Velocity","velocity.slope", "Velocity.intercept","SV30.intercept","SV30.slope","SV30","DSVI")]


Parameters[nrow(Parameters)+1,] <-c(Date,Dilution.percent,n,SS,velocity, velocity.slope, Velocity.intercept, SV_30_intercept,SV_30_slope,SV_30,DSVI)
parameterName <- paste(path_out, "Biofos_timeseries_parameters.csv", sep = "")
```

```{r}
write.csv(Parameters, parameterName)
```



# timeseries: https://r-graph-gallery.com/time-series.html
