---
title: "Broad_investigation_collected"
author: "Vibeke S. Nielsen"
date: "2022-11-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Save file to
```{r}
path_out<- "D://Speciale/Data/Broad_inspection/"
fileName <- paste(path_out, "Analysis", sep = "")
```



#Install packages
```{r}
library(data.table)
library(readxl)
library(tidyverse)
library(ggplot2)
library(plyr)
library(dplyr)
library(ggpubr)

```



#Loading data

```{r}
Mariagerfjord100 <- read.csv( "D://Speciale/Data/Broad_inspection/Mariagerfjord100.csv")
Mariagerfjord75 <- read.csv( "D://Speciale/Data/Broad_inspection/Mariagerfjord75.csv")
Mariagerfjord50 <- read.csv( "D://Speciale/Data/Broad_inspection/Mariagerfjord50.csv")

Mariagerfjord <- Mariagerfjord100 %>%
  mutate(set = factor(1)) %>%
  rbind(Mariagerfjord75 %>%
          mutate(set = factor(2))) %>%
  rbind(Mariagerfjord50 %>%
          mutate(set = factor(3))) 

Hjørring100 <- read.csv( "D://Speciale/Data/Broad_inspection/Hjørring100.csv")
Hjørring75 <- read.csv( "D://Speciale/Data/Broad_inspection/Hjørring75.csv")
Hjørring50 <- read.csv( "D://Speciale/Data/Broad_inspection/Hjørring50.csv")

Hjørring <- Hjørring100 %>%
  mutate(set = factor(1)) %>%
  rbind(Hjørring75 %>%
          mutate(set = factor(2))) %>%
  rbind(Hjørring50 %>%
          mutate(set = factor(3))) 

Hirtshals100 <- read.csv( "D://Speciale/Data/Broad_inspection/Hirtshals100.csv")
Hirtshals75 <- read.csv( "D://Speciale/Data/Broad_inspection/Hirtshals75.csv")
Hirtshals50 <- read.csv( "D://Speciale/Data/Broad_inspection/Hirtshals50.csv")

Hirtshals <- Hirtshals100 %>%
  mutate(set = factor(1)) %>%
  rbind(Hirtshals75 %>%
          mutate(set = factor(2))) %>%
  rbind(Hirtshals50 %>%
          mutate(set = factor(3))) 

Frederecia100 <- read.csv( "D://Speciale/Data/Broad_inspection/Frederecia100.csv")
Frederecia75 <- read.csv( "D://Speciale/Data/Broad_inspection/Frederecia75.csv")
Frederecia50 <- read.csv( "D://Speciale/Data/Broad_inspection/Frederecia50.csv")

Frederecia <- Frederecia100 %>%
  mutate(set = factor(1)) %>%
  rbind(Frederecia75 %>%
          mutate(set = factor(2))) %>%
  rbind(Frederecia50 %>%
          mutate(set = factor(3))) 

Viborg100 <- read.csv( "D://Speciale/Data/Broad_inspection/Viborg100.csv")
Viborg75 <- read.csv( "D://Speciale/Data/Broad_inspection/Viborg75.csv")
Viborg50 <- read.csv( "D://Speciale/Data/Broad_inspection/Viborg50.csv")

Viborg <- Viborg100 %>%
  mutate(set = factor(1)) %>%
  rbind(Viborg75 %>%
          mutate(set = factor(2))) %>%
  rbind(Viborg50 %>%
          mutate(set = factor(3))) 

Viby100 <- read.csv( "D://Speciale/Data/Broad_inspection/Viby100.csv")
Viby75 <- read.csv( "D://Speciale/Data/Broad_inspection/Viby75.csv")
Viby50 <- read.csv( "D://Speciale/Data/Broad_inspection/Viby50.csv")

Viby <- Viby100 %>%
  mutate(set = factor(1)) %>%
  rbind(Viby75 %>%
          mutate(set = factor(2))) %>%
  rbind(Viby50 %>%
          mutate(set = factor(3))) 

Egå100 <- read.csv( "D://Speciale/Data/Broad_inspection/Egå100.csv")
Egå75 <- read.csv( "D://Speciale/Data/Broad_inspection/Egå75.csv")
Egå50 <- read.csv( "D://Speciale/Data/Broad_inspection/Egå50.csv")

Egå <- Egå100 %>%
  mutate(set = factor(1)) %>%
  rbind(Egå75 %>%
          mutate(set = factor(2))) %>%
  rbind(Egå50 %>%
          mutate(set = factor(3))) 

Silkeborg100 <- read.csv( "D://Speciale/Data/Broad_inspection/Silkeborg100.csv")
Silkeborg75 <- read.csv( "D://Speciale/Data/Broad_inspection/Silkeborg75.csv")
Silkeborg50 <- read.csv( "D://Speciale/Data/Broad_inspection/Silkeborg50.csv")

Silkeborg <- Silkeborg100 %>%
  mutate(set = factor(1)) %>%
  rbind(Silkeborg75 %>%
          mutate(set = factor(2))) %>%
  rbind(Silkeborg50 %>%
          mutate(set = factor(3))) 

Randers100 <- read.csv( "D://Speciale/Data/Broad_inspection/Randers100.csv")
Randers75 <- read.csv( "D://Speciale/Data/Broad_inspection/Randers75.csv")
Randers50 <- read.csv( "D://Speciale/Data/Broad_inspection/Randers50.csv")

Randers <- Randers100 %>%
  mutate(set = factor(1)) %>%
  rbind(Randers75 %>%
          mutate(set = factor(2))) %>%
  rbind(Randers50 %>%
          mutate(set = factor(3))) 

Skagen100 <- read.csv( "D://Speciale/Data/Broad_inspection/Skagen100.csv")
Skagen75 <- read.csv( "D://Speciale/Data/Broad_inspection/Skagen75.csv")
Skagen50 <- read.csv( "D://Speciale/Data/Broad_inspection/Skagen50.csv")

Skagen <- Skagen100 %>%
  mutate(set = factor(1)) %>%
  rbind(Skagen75 %>%
          mutate(set = factor(2))) %>%
  rbind(Skagen50 %>%
          mutate(set = factor(3))) 



Parameters <- read.csv( "D://Speciale/Data/Broad_inspection/Collected_parameters_process.csv")
Parameters <- Parameters[,2:13]

```

##Create plots
```{r}
Mariagerfjord_plot <- ggplot(data =Mariagerfjord, mapping=aes(x=Timestamp, y=Height)) + geom_point(aes(color = set))+labs(x="Time [s]", y="Sludge blanket height [mm]")+ guides(color=guide_legend("Dilution")) + ggtitle("Mariagerfjord")+ geom_abline(intercept = Parameters[(Parameters[,"Test.name"]) == "Mariagerfjord", "Velocity.intercept"], slope = Parameters[(Parameters[,"Test.name"]) == "Mariagerfjord", "Velocity.slope"], color=c("blue","green","red"))

Mariagerfjord_plot



Hjørring_plot <- ggplot(data =Hjørring, mapping=aes(x=Timestamp, y=Height)) + geom_point(aes(color = set))+labs(x="Time [s]", y="Sludge blanket height [mm]")+ guides(color=guide_legend("Dilution")) + ggtitle("Hjørring")+ geom_abline(intercept = Parameters[(Parameters[,"Test.name"]) == "Hjørring", "Velocity.intercept"], slope = Parameters[(Parameters[,"Test.name"]) == "Hjørring", "Velocity.slope"],color=c("blue","green","red"))

Hjørring_plot
plotName <- paste(path_out, "Hjørringplot.png")
ggsave(plotName, width = 10, height = 5)

Hirtshals_plot <- ggplot(data =Hirtshals, mapping=aes(x=Timestamp, y=Height)) + geom_point(aes(color = set))+labs(x="Time [s]", y="Sludge blanket height [mm]")+ guides(color=guide_legend("Dilution")) + ggtitle("Hirtshals")+ geom_abline(intercept = Parameters[(Parameters[,"Test.name"]) == "Hirtshals", "Velocity.intercept"], slope = Parameters[(Parameters[,"Test.name"]) == "Hirtshals", "Velocity.slope"],color=c("blue","green","red"))

Hirtshals_plot

Frederecia_plot <- ggplot(data =Frederecia, mapping=aes(x=Timestamp, y=Height)) + geom_point(aes(color = set))+labs(x="Time [s]", y="Sludge blanket height [mm]")+ guides(color=guide_legend("Dilution")) + ggtitle("Frederecia")+ geom_abline(intercept = Parameters[(Parameters[,"Test.name"]) == "Frederecia", "Velocity.intercept"], slope = Parameters[(Parameters[,"Test.name"]) == "Frederecia", "Velocity.slope"],color=c("blue","green","red"))

Frederecia_plot 

Viborg_plot <- ggplot(data =Viborg, mapping=aes(x=Timestamp, y=Height)) + geom_point(aes(color = set))+labs(x="Time [s]", y="Sludge blanket height [mm]")+ guides(color=guide_legend("Dilution")) + ggtitle("Viborg")#+ geom_abline(intercept = Parameters[(Parameters[,"Test.name"]) == "Viborg", "Velocity.intercept"], slope = Parameters[(Parameters[,"Test.name"]) == "Viborg", "Velocity.slope"],color=c("blue","green","red"))


Viborg_plot

Viby_plot <- ggplot(data =Viby, mapping=aes(x=Timestamp, y=Height)) + geom_point(aes(color = set))+labs(x="Time [s]", y="Sludge blanket height [mm]")+ guides(color=guide_legend("Dilution")) + ggtitle("Viby")+ geom_abline(intercept = Parameters[(Parameters[,"Test.name"]) == "Viby", "Velocity.intercept"], slope = Parameters[(Parameters[,"Test.name"]) == "Viby", "Velocity.slope"],color=c("blue","green","red"))


Viby_plot

Egå_plot <- ggplot(data =Egå, mapping=aes(x=Timestamp, y=Height)) + geom_point(aes(color = set))+labs(x="Time [s]", y="Sludge blanket height [mm]")+ guides(color=guide_legend("Dilution")) + ggtitle("Egå")+ geom_abline(intercept = Parameters[(Parameters[,"Test.name"]) == "Egå", "Velocity.intercept"], slope = Parameters[(Parameters[,"Test.name"]) == "Egå", "Velocity.slope"],color=c("blue","green","red"))


Egå_plot

Silkeborg_plot <- ggplot(data =Silkeborg, mapping=aes(x=Timestamp, y=Height)) + geom_point(aes(color = set))+labs(x="Time [s]", y="Sludge blanket height [mm]")+ guides(color=guide_legend("Dilution")) + ggtitle("Silkeborg")+ geom_abline(intercept = Parameters[(Parameters[,"Test.name"]) == "Silkeborg" & (Parameters[,"Dilution.percent"]) == 75, "Velocity.intercept"], slope = Parameters[(Parameters[,"Test.name"]) == "Silkeborg" & (Parameters[,"Dilution.percent"]) == 75, "Velocity.slope"],color="green") + geom_abline(intercept = Parameters[(Parameters[,"Test.name"]) == "Silkeborg" & (Parameters[,"Dilution.percent"]) == 50, "Velocity.intercept"], slope = Parameters[(Parameters[,"Test.name"]) == "Silkeborg" & (Parameters[,"Dilution.percent"]) == 50, "Velocity.slope"],color="blue")


Silkeborg_plot

Randers_plot <- ggplot(data =Randers, mapping=aes(x=Timestamp, y=Height)) + geom_point(aes(color = set))+labs(x="Time [s]", y="Sludge blanket height [mm]")+ guides(color=guide_legend("Dilution")) + ggtitle("Randers")#+ geom_abline(intercept = Parameters[(Parameters[,"Test.name"]) == "Randers", "Velocity.intercept"], slope = Parameters[(Parameters[,"Test.name"]) == "Randers", "Velocity.slope"],color=set)

Randers_plot

Skagen_plot <- ggplot(data =Skagen, mapping=aes(x=Timestamp, y=Height)) + geom_point(aes(color = set))+labs(x="Time [s]", y="Sludge blanket height [mm]")+ guides(color=guide_legend("Dilution")) + ggtitle("Skagen")+ geom_abline(intercept = Parameters[(Parameters[,"Test.name"]) == "Skagen", "Velocity.intercept"], slope = Parameters[(Parameters[,"Test.name"]) == "Skagen", "Velocity.slope"],color=c("blue","green","red"))

Skagen_plot

```

#Display velocities
```{r}
Velocity_plot <- ggplot(
    data = Parameters, 
    mapping = aes(
      x = Dilution.percent,
      y = Velocity,
      color = factor(Dilution.percent)
    )
  )+ geom_point(aes())+ geom_smooth(method="lm",se=F, formula = Parameters$Velocity~Parameters$Dilution.percent) + facet_wrap(
    ~ factor(Test.name),    nrow = 2
  )+ xlim(0, 100) + guides(color=guide_legend("Sludge content [%]"))  + labs( x="Sludge content [%]", y="Settling velocity [mm/s]") + theme(
  axis.text.x = element_blank())+ ggtitle("Settling velocity") #+ scale_y_continuous(breaks = round(seq(min(Parameters$Velocity), max(Parameters$Velocity), by = 0.1),1))

Velocity_plot

  
```
#Shown in sludge concentration and velocity in m/h
```{r}
Parameters$Concentration <- 
      Parameters$SS * Parameters$Dilution.percent / 100
Parameters$NewVelocity <- Parameters$Velocity/1000*3600

NewVelocity_plot <- ggplot(
    data = Parameters, 
    mapping = aes(
      x = Concentration,
      y = NewVelocity,
      color = factor(Dilution.percent)
    )
  )+ geom_point(aes())+ geom_smooth(method="lm",se=F, formula = Parameters$NewVelocity~Parameters$Concentration) + facet_wrap(
    ~ factor(Test.name),    nrow = 2
  )+ xlim(0, 8) + guides(color=guide_legend("Sludge content [%]"))  + labs( x="Sludge Concentration [g/L]", y="Hindered settling velocity [m/h]") + scale_y_continuous(breaks = round(seq(min(Parameters$NewVelocity), max(Parameters$NewVelocity), by = 1),0.5))+ ggtitle("Settling velocity")

NewVelocity_plot
plotName <- paste(path_out, "Velocityplot_units.png")
ggsave(plotName, width = 7.5, height = 5)

```

#Shown in sludge concentration and velocity in m/h
```{r}
#interval
V_interval <- subset(Parameters, Concentration >= 2.5 & Concentration <= 3.1)


V_intervalplot <- ggplot(
    data = V_interval , 
    mapping = aes(
      x = Concentration,
      y = NewVelocity,
      color = factor(Dilution.percent)
    )
  )+ geom_point(aes())+ geom_smooth(method="lm",se=F, formula = V_interval$NewVelocity~V_interval$Concentration) + 
  #facet_wrap(  ~ factor(Test.name),    nrow = 2)+ 
  xlim(2, 4) + guides(color=guide_legend("Sludge content [%]"))  + labs( x="Sludge Concentration [g/L]", y="Hindered settling velocity [m/h]") + scale_y_continuous(breaks = round(seq(min(V_interval$NewVelocity), max(V_interval$NewVelocity), by = 1),0.5))+ ggtitle("Settling velocity")

V_intervalplot
plotName <- paste(path_out, "V_intervalplot.png")
ggsave(plotName, width = 7.5, height = 5)

```




#Fitting Vesilind curves to velocity
```{r}
Vesilind_curve <- function(r_V, V_0, X_TSS) (V_0*exp(-r_V*X_TSS))
Takacs_curve <- function(V_0, r_h, f_hs, r_f, X_TSS) (V_0*(exp(-r_h*(X_TSS-f_hs*X_TSS))-exp(-r_f*(X_TSS-f_hs*X_TSS))))

```
##Fitting Hjørring curve
```{r}
X_TSS <- Parameters[(Parameters[,"Test.name"]) == "Hjørring", "Concentration"]

Hjørring_subset <- subset(Parameters[(Parameters[,"Test.name"]) == "Hjørring",])

fit_hjørring <- nls(NewVelocity ~ Vesilind_curve(r_V, V_0, X_TSS), data=Hjørring_subset, start=list(r_V=0.5,V_0=10))

summary(fit_hjørring)

cc <- coef(fit_hjørring)
r_Vfit <- cc["r_V"]
V_0fit <- cc["V_0"]
X_TSSfine <- 0.1*c(0:100)
df_X_TSSfine <- as.data.frame(X_TSSfine)

Fit_curve_Hjørring <- ggplot(data =Hjørring_subset, mapping=aes(x=Concentration, y=NewVelocity)) + geom_point(aes())+labs(x="Concentration [g/L]", y="Velocity [m/h]")+ ggtitle("Vesilind curve fit: Hjørring")+scale_x_continuous(limits = c(0, 10))+scale_y_continuous(limits = c(0, 20))+ geom_line(data= df_X_TSSfine, aes(x=X_TSSfine, y = Vesilind_curve(X_TSSfine,V_0fit,r_Vfit)))
Fit_curve_Hjørring

Results_Hjørring <- summary(fit_hjørring)$coefficients
Results_Hjørring <- as.data.frame(Results_Hjørring)
Results_Hjørring <- cbind(rownames(Results_Hjørring), data.frame(Results_Hjørring, row.names=NULL))
names(Results_Hjørring)[1] <- "Parameter"
Test.name <- c("Hjørring", "Hjørring")
Results_Hjørring <- cbind(Test.name, Results_Hjørring)

```



##Fitting Skagen curve
```{r}
X_TSS <- Parameters[(Parameters[,"Test.name"]) == "Skagen", "Concentration"]

Skagen_subset <- subset(Parameters[(Parameters[,"Test.name"]) == "Skagen",])

fit_Skagen <- nls(NewVelocity ~ Vesilind_curve(r_V, V_0, X_TSS), data=Skagen_subset, start=list(r_V=0.5,V_0=10))

summary(fit_Skagen)

cc <- coef(fit_Skagen)
r_Vfit <- cc["r_V"]
V_0fit <- cc["V_0"]
X_TSSfine <- 0.1*c(0:100)
df_X_TSSfine <- as.data.frame(X_TSSfine)

Fit_curve_Skagen <- ggplot(data =Skagen_subset, mapping=aes(x=Concentration, y=NewVelocity)) + geom_point(aes())+labs(x="Concentration [g/L]", y="Velocity [m/h]")+ ggtitle("Vesilind curve fit: Skagen")+scale_x_continuous(limits = c(0, 12))+scale_y_continuous(limits = c(0, 12))+ geom_line(data= df_X_TSSfine, aes(x=X_TSSfine, y = Vesilind_curve(X_TSSfine,V_0fit,r_Vfit)))
Fit_curve_Skagen

Results_Skagen <- summary(fit_Skagen)$coefficients
Results_Skagen <- as.data.frame(Results_Skagen)
Results_Skagen <- cbind(rownames(Results_Skagen), data.frame(Results_Skagen, row.names=NULL))
names(Results_Skagen)[1] <- "Parameter"
Test.name <- c("Skagen", "Skagen")
Results_Skagen <- cbind(Test.name, Results_Skagen)

```


##Fitting Mariagerfjord curve
```{r}
X_TSS <- Parameters[(Parameters[,"Test.name"]) == "Mariagerfjord", "Concentration"]

Mariagerfjord_subset <- subset(Parameters[(Parameters[,"Test.name"]) == "Mariagerfjord",])

fit_Mariagerfjord <- nls(NewVelocity ~ Vesilind_curve(r_V, V_0, X_TSS), data=Mariagerfjord_subset, start=list(r_V=0.5,V_0=10))

summary(fit_Mariagerfjord)

cc <- coef(fit_Mariagerfjord)
r_Vfit <- cc["r_V"]
V_0fit <- cc["V_0"]
X_TSSfine <- 0.1*c(0:100)
df_X_TSSfine <- as.data.frame(X_TSSfine)

Fit_curve_Mariagerfjord <- ggplot(data =Mariagerfjord_subset, mapping=aes(x=Concentration, y=NewVelocity)) + geom_point(aes())+labs(x="Concentration [g/L]", y="Velocity [m/h]")+ ggtitle("Vesilind curve fit: Mariagerfjord")+scale_x_continuous(limits = c(0, 12))+scale_y_continuous(limits = c(0, 12))+ geom_line(data= df_X_TSSfine, aes(x=X_TSSfine, y = Vesilind_curve(X_TSSfine,V_0fit,r_Vfit)))
Fit_curve_Mariagerfjord

Results_Mariagerfjord <- summary(fit_Mariagerfjord)$coefficients
Results_Mariagerfjord <- as.data.frame(Results_Mariagerfjord)
Results_Mariagerfjord <- cbind(rownames(Results_Mariagerfjord), data.frame(Results_Mariagerfjord, row.names=NULL))
names(Results_Mariagerfjord)[1] <- "Parameter"
Test.name <- c("Mariagerfjord", "Mariagerfjord")
Results_Mariagerfjord <- cbind(Test.name, Results_Mariagerfjord)

```

##Fitting Egå curve
```{r}
X_TSS <- Parameters[(Parameters[,"Test.name"]) == "Egå", "Concentration"]

Egå_subset <- subset(Parameters[(Parameters[,"Test.name"]) == "Egå",])

fit_Egå <- nls(NewVelocity ~ Vesilind_curve(r_V, V_0, X_TSS), data=Egå_subset, start=list(r_V=0.5,V_0=10))

summary(fit_Egå)

cc <- coef(fit_Egå)
r_Vfit <- cc["r_V"]
V_0fit <- cc["V_0"]
X_TSSfine <- 0.1*c(0:100)
df_X_TSSfine <- as.data.frame(X_TSSfine)

Fit_curve_Egå <- ggplot(data =Egå_subset, mapping=aes(x=Concentration, y=NewVelocity)) + geom_point(aes())+labs(x="Concentration [g/L]", y="Velocity [m/h]")+ ggtitle("Vesilind curve fit: Egå")+scale_x_continuous(limits = c(0, 12))+scale_y_continuous(limits = c(0, 25))+ geom_line(data= df_X_TSSfine, aes(x=X_TSSfine, y = Vesilind_curve(X_TSSfine,V_0fit,r_Vfit)))
Fit_curve_Egå

Results_Egå <- summary(fit_Egå)$coefficients
Results_Egå <- as.data.frame(Results_Egå)
Results_Egå <- cbind(rownames(Results_Egå), data.frame(Results_Egå, row.names=NULL))
names(Results_Egå)[1] <- "Parameter"
Test.name <- c("Egå", "Egå")
Results_Egå <- cbind(Test.name, Results_Egå)
```

##Fitting Viby curve
```{r}
X_TSS <- Parameters[(Parameters[,"Test.name"]) == "Viby", "Concentration"]

Viby_subset <- subset(Parameters[(Parameters[,"Test.name"]) == "Viby",])

fit_Viby <- nls(NewVelocity ~ Vesilind_curve(r_V, V_0, X_TSS), data=Viby_subset, start=list(r_V=0.5,V_0=10))

summary(fit_Viby)

cc <- coef(fit_Viby)
r_Vfit <- cc["r_V"]
V_0fit <- cc["V_0"]
X_TSSfine <- 0.1*c(0:100)
df_X_TSSfine <- as.data.frame(X_TSSfine)

Fit_curve_Viby <- ggplot(data =Viby_subset, mapping=aes(x=Concentration, y=NewVelocity)) + geom_point(aes())+labs(x="Concentration [g/L]", y="Velocity [m/h]")+ ggtitle("Vesilind curve fit: Viby")+scale_x_continuous(limits = c(0, 12))+scale_y_continuous(limits = c(0, 12))+ geom_line(data= df_X_TSSfine, aes(x=X_TSSfine, y = Vesilind_curve(X_TSSfine,V_0fit,r_Vfit)))
Fit_curve_Viby

Results_Viby <- summary(fit_Viby)$coefficients
Results_Viby <- as.data.frame(Results_Viby)
Results_Viby <- cbind(rownames(Results_Viby), data.frame(Results_Viby, row.names=NULL))
names(Results_Viby)[1] <- "Parameter"
Test.name <- c("Viby", "Viby")
Results_Viby <- cbind(Test.name, Results_Viby)

```

##Fitting Viborg curve
```{r}
X_TSS <- Parameters[(Parameters[,"Test.name"]) == "Viborg"&(Parameters[,"Date"]) == "31.01.2023", "SS"]

Viborg_subset <- subset(Parameters[(Parameters[,"Test.name"]) == "Viborg"&(Parameters[,"Date"]) == "31.01.2023",])

fit_Viborg <- nls(NewVelocity ~ Vesilind_curve(r_V, V_0, X_TSS), data=Viborg_subset, start=list(r_V=0.5,V_0=10))

summary(fit_Viborg)

cc <- coef(fit_Viborg)
r_Vfit <- cc["r_V"]
V_0fit <- cc["V_0"]
X_TSSfine <- 0.1*c(0:100)
df_X_TSSfine <- as.data.frame(X_TSSfine)

Fit_curve_Viborg <- ggplot(data =Viborg_subset, mapping=aes(x=Concentration, y=NewVelocity)) + geom_point(aes())+labs(x="Concentration [g/L]", y="Velocity [m/h]")+ ggtitle("Vesilind curve fit: Viborg")+scale_x_continuous(limits = c(0, 12))+scale_y_continuous(limits = c(0, 12))+ geom_line(data= df_X_TSSfine, aes(x=X_TSSfine, y = Vesilind_curve(X_TSSfine,V_0fit,r_Vfit)))
Fit_curve_Viborg

Results_Viborg <- summary(fit_Viborg)$coefficients
Results_Viborg <- as.data.frame(Results_Viborg)
Results_Viborg <- cbind(rownames(Results_Viborg), data.frame(Results_Viborg, row.names=NULL))
names(Results_Viborg)[1] <- "Parameter"
Test.name <- c("Viborg", "Viborg")
Results_Viborg <- cbind(Test.name, Results_Viborg)
```
##Fitting Hirtshals curve
```{r}
X_TSS <- Parameters[(Parameters[,"Test.name"]) == "Hirtshals", "Concentration"]

Hirtshals_subset <- subset(Parameters[(Parameters[,"Test.name"]) == "Hirtshals",])

fit_Hirtshals <- nls(NewVelocity ~ Vesilind_curve(r_V, V_0, X_TSS), data=Hirtshals_subset, start=list(r_V=0.5,V_0=10))

summary(fit_Hirtshals)

cc <- coef(fit_Hirtshals)
r_Vfit <- cc["r_V"]
V_0fit <- cc["V_0"]
X_TSSfine <- 0.1*c(0:100)
df_X_TSSfine <- as.data.frame(X_TSSfine)

Fit_curve_Hirtshals <- ggplot(data =Hirtshals_subset, mapping=aes(x=Concentration, y=NewVelocity)) + geom_point(aes())+labs(x="Concentration [g/L]", y="Velocity [m/h]")+ ggtitle("Vesilind curve fit: Hirtshals")+scale_x_continuous(limits = c(0, 12))+scale_y_continuous(limits = c(0, 16))+ geom_line(data= df_X_TSSfine, aes(x=X_TSSfine, y = Vesilind_curve(X_TSSfine,V_0fit,r_Vfit)))
Fit_curve_Hirtshals

Results_Hirtshals <- summary(fit_Hirtshals)$coefficients
Results_Hirtshals <- as.data.frame(Results_Hirtshals)
Results_Hirtshals <- cbind(rownames(Results_Hirtshals), data.frame(Results_Hirtshals, row.names=NULL))
names(Results_Hirtshals)[1] <- "Parameter"
Test.name <- c("Hirtshals", "Hirtshals")
Results_Hirtshals <- cbind(Test.name, Results_Hirtshals)

```

##Fitting Frederecia curve
```{r}
X_TSS <- Parameters[(Parameters[,"Test.name"]) == "Frederecia", "Concentration"]

Frederecia_subset <- subset(Parameters[(Parameters[,"Test.name"]) == "Frederecia",])

fit_Frederecia <- nls(NewVelocity ~ Vesilind_curve(r_V, V_0, X_TSS), data=Frederecia_subset, start=list(r_V=0.5,V_0=10))

summary(fit_Frederecia)

cc <- coef(fit_Frederecia)
r_Vfit <- cc["r_V"]
V_0fit <- cc["V_0"]
X_TSSfine <- 0.1*c(0:100)
df_X_TSSfine <- as.data.frame(X_TSSfine)

Fit_curve_Frederecia <- ggplot(data =Frederecia_subset, mapping=aes(x=Concentration, y=NewVelocity)) + geom_point(aes())+labs(x="Concentration [g/L]", y="Velocity [m/h]")+ ggtitle("Vesilind curve fit: Frederecia")+scale_x_continuous(limits = c(0, 12))+scale_y_continuous(limits = c(0, 25))+ geom_line(data= df_X_TSSfine, aes(x=X_TSSfine, y = Vesilind_curve(X_TSSfine,V_0fit,r_Vfit)))
Fit_curve_Frederecia

Results_Frederecia <- summary(fit_Frederecia)$coefficients
Results_Frederecia <- as.data.frame(Results_Frederecia)
Results_Frederecia <- cbind(rownames(Results_Frederecia), data.frame(Results_Frederecia, row.names=NULL))
names(Results_Frederecia)[1] <- "Parameter"
Test.name <- c("Frederecia", "Frederecia")
Results_Frederecia <- cbind(Test.name, Results_Frederecia)

```


##Fitting Randers curve
```{r}
X_TSS <- Parameters[(Parameters[,"Test.name"]) == "Randers", "Concentration"]

Randers_subset <- subset(Parameters[(Parameters[,"Test.name"]) == "Randers",])

fit_Randers <- nls(NewVelocity ~ Vesilind_curve(r_V, V_0, X_TSS), data=Randers_subset, start=list(r_V=0.5,V_0=10))

summary(fit_Randers)

cc <- coef(fit_Randers)
r_Vfit <- cc["r_V"]
V_0fit <- cc["V_0"]
X_TSSfine <- 0.1*c(0:100)
df_X_TSSfine <- as.data.frame(X_TSSfine)

Fit_curve_Randers <- ggplot(data =Randers_subset, mapping=aes(x=Concentration, y=NewVelocity)) + geom_point(aes())+labs(x="Concentration [g/L]", y="Velocity [m/h]")+ ggtitle("Vesilind curve fit: Randers")+scale_x_continuous(limits = c(0, 12))+scale_y_continuous(limits = c(0, 12))+ geom_line(data= df_X_TSSfine, aes(x=X_TSSfine, y = Vesilind_curve(X_TSSfine,V_0fit,r_Vfit)))
Fit_curve_Randers

Results_Randers <- summary(fit_Randers)$coefficients
Results_Randers <- as.data.frame(Results_Randers)
Results_Randers <- cbind(rownames(Results_Randers), data.frame(Results_Randers, row.names=NULL))
names(Results_Randers)[1] <- "Parameter"
Test.name <- c("Randers", "Randers")
Results_Randers <- cbind(Test.name, Results_Randers)
```

##Fitting Silkeborg curve
```{r}
#X_TSS <- Parameters[(Parameters[,"Test.name"]) == "Silkeborg", "Concentration"]

#Silkeborg_subset <- subset(Parameters[(Parameters[,"Test.name"]) == "Silkeborg",])

#fit_Silkeborg <- nls(NewVelocity ~ Vesilind_curve(r_V, V_0, X_TSS), data=Silkeborg_subset, start=list(r_V=0.5,V_0=10))

#summary(fit_Silkeborg)

#cc <- coef(fit_Silkeborg)
#r_Vfit <- cc["r_V"]
#V_0fit <- cc["V_0"]
#X_TSSfine <- 0.1*c(0:100)
#df_X_TSSfine <- as.data.frame(X_TSSfine)

#Fit_curve_Silkeborg <- ggplot(data =Silkeborg_subset, mapping=aes(x=Concentration, y=NewVelocity)) + geom_point(aes())+labs(x="Concentration [g/L]", y="Velocity [m/h]")+ ggtitle("Vesilind curve fit: Silkeborg")+scale_x_continuous(limits = c(0, 12))+scale_y_continuous(limits = c(0, 12))+ geom_line(data= df_X_TSSfine, aes(x=X_TSSfine, y = Vesilind_curve(X_TSSfine,V_0fit,r_Vfit)))
#Fit_curve_Silkeborg

```
##Gather fitting parameters
```{r}
Fitting_results <- rbind(Results_Egå, Results_Frederecia, Results_Hirtshals, Results_Hjørring, Results_Mariagerfjord, Results_Skagen, Results_Randers, Results_Viby, Results_Viborg)
names(Fitting_results)[6] <- "P_value"
names(Fitting_results)[5] <- "t_value"
names(Fitting_results)[4] <- "Std.error"
names(Fitting_results)[1] <- "Plant"

V_0collected <- subset(Fitting_results[(Fitting_results[,"Parameter"]) == "V_0",])
r_Vcollected  <- subset(Fitting_results[(Fitting_results[,"Parameter"]) == "r_V",])


v_0estimate <- ggplot()+ 
  geom_pointrange(data = V_0collected,  mapping = aes( x = Plant, y = Estimate)) +
  scale_y_continuous(limits = c(0, 25), breaks = seq(0, 25, 5))+ggtitle("V_0 ")+ 
  theme(axis.text.x = element_text(angle = 90),axis.title.x = element_blank())
v_0Pvalue <- ggplot()+ 
  geom_point(data = V_0collected,  mapping = aes( x = Plant, y = P_value)) +
  scale_y_continuous(limits = c(0, 0.6), breaks = seq(0, 6, 0.1))+
  geom_hline(yintercept=0.05, linetype="dashed", color = "blue")+ggtitle("V_0")+ 
  theme(axis.text.x = element_text(angle = 90),axis.title.x = element_blank())
r_Vestimate <- ggplot()+ 
  geom_point(data = r_Vcollected,  mapping = aes( x = Plant, y = Estimate)) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2))+ggtitle("r_V ")+ 
  theme(axis.text.x = element_text(angle = 90),axis.title.x = element_blank())
r_VPvalue <- ggplot()+ 
  geom_point(data = r_Vcollected,  mapping = aes( x = Plant, y = P_value)) + 
  scale_y_continuous(limits = c(0, 0.6), breaks = seq(0, 6, 0.1))+
  geom_hline(yintercept=0.05, linetype="dashed", color = "blue")+ggtitle("r_V ")+ 
  theme(axis.text.x = element_text(angle = 90),axis.title.x = element_blank())

ggarrange(v_0estimate, r_Vestimate,v_0Pvalue, r_VPvalue, labels = c("A", "B","C", "D"), ncol = 2, nrow = 2)
ggarrange(v_0Pvalue, r_VPvalue, ncol = 1, nrow = 2)

```


#Display SV30

```{r}

SV30_plot <- ggplot(
    data = Parameters, 
    mapping = aes(
      x = Concentration,
      y = SV30,
      color = factor(Dilution.percent)
    )
  )+ geom_point(aes())+ facet_wrap(
    ~ factor(Test.name),    nrow = 2
  )+ xlim(0, 8) + guides(color=guide_legend("Sludge content [%]"))  + labs( x="Sludge concentration [g/L]", y="Sludge volume after 30 min [mL/L]") + scale_y_continuous(breaks = c(0,100,200,300,400,500,600,700,800,900)) + ggtitle("SV30")

SV30_plot
plotName <- paste(path_out, "SV30plot.png")
ggsave(plotName, width = 7.5, height = 5)
  
```




#Display DSVI's
```{r}
DSVIinterval <- subset(Parameters[(Parameters[,"SV30"]) >=150,])
DSVIinterval <- subset(DSVIinterval[(DSVIinterval[,"SV30"]) <=250,])

DSVIinterval_plot <- ggplot(
    data = DSVIinterval, 
    mapping = aes(
      x = Concentration,
      y = DSVI
    )
  )+ geom_point(aes()) + facet_wrap(
    ~ factor(Test.name),    nrow = 2
  )+ xlim(0, 6) + guides(color=guide_legend("Sludge content [%]"))  + labs( x="Sludge concentration [g/L]", y="Diluted sludge volume index [mL/g]") + scale_y_continuous(breaks = round(seq(min(0), max(350), by = 50),1))+ ggtitle("DSVI")

DSVIinterval_plot
plotName <- paste(path_out, "DSVIintervalplot.png")
ggsave(plotName, width = 7.5, height = 5)


DSVI_plot <- ggplot(
    data = Parameters, 
    mapping = aes(
      x = Concentration,
      y = DSVI,
      color = factor(Dilution.percent)
    )
  )+ geom_point(aes()) + facet_wrap(
    ~ factor(Test.name),    nrow = 2
  )+ xlim(0, 8) + guides(color=guide_legend("Sludge content [%]"))  + labs( x="Sludge concentration [g/L]", y="Diluted sludge volume index [mL/L]") + scale_y_continuous(breaks = round(seq(min(150), max(250), by = 10),1))+ ggtitle("DSVI")

DSVI_plot
plotName <- paste(path_out, "DSVIplot.png")
ggsave(plotName, width = 7.5, height = 5)

```


#Write out files
```{r}
parameterName <- paste(path_out, "Collected_parameters.csv", sep = "")
write.csv(Parameters, parameterName)


```

